\documentclass[12pt]{article}
\usepackage{geometry}
\geometry{a4paper, margin=1in}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{hyperref}

\title{SenseAPI Validation Report}
\author{Senior Godot Engine Architect & AI Integration Specialist}
\date{\today}

\begin{document}

\maketitle

\section{Introduction}
This report outlines the implementation of a persistent Idle State and the \texttt{SenseAPI} for the Godot Core architecture. This allows the AI Planning Team to transition the engine from a ``Command-Only'' flow to a robust ``Sense-Think-Act'' cycle without needing to hold direct references to physical scene nodes.

\section{Unit Idle State \& Busy-Check Logic}
The \texttt{Unit.gd} script natively updates an \texttt{is\_idle} boolean. When the underlying \texttt{CommandQueue} runs dry, the \texttt{Unit} emits a \texttt{unit\_idled(unit\_id)} signal. The \texttt{ActionGateway} relays this signal to the broader AI context.
\begin{itemize}
    \item \textbf{Transition to BUSY:} The unit marks \texttt{is\_idle = false} the moment \texttt{ActionGateway} feeds its \texttt{CommandQueue} and triggers active execution.
    \item \textbf{Transition to IDLE:} After completing the final step in a plan and emptying the queue, \texttt{is\_idle = true} is applied.
\end{itemize}

\subsection{State Flow Visual Reference}
\begin{verbatim}
ActionState Enum Integration
[PENDING] -> [RUNNING] -> [COMPLETED / FAILED] -> [IDLE (Queue Empty)]
\end{verbatim}

\section{Sense API Reference}
Responses are exclusively serialized as \texttt{Dictionary} or \texttt{Array} objects to satisfy security requirements and prevent malicious Node manipulations.

\begin{table}[h]
\centering
\renewcommand{\arraystretch}{1.5}
\begin{tabularx}{\textwidth}{@{}lXl@{}}
\toprule
\textbf{Method} & \textbf{Description} & \textbf{Return Value} \\
\midrule
\texttt{get\_all\_units()} & Returns all units in play. & \texttt{Array[Dictionary]} \\
\texttt{get\_unit\_status(uid)} & Snapshot including ActionState context. & \texttt{Dictionary} \\
\texttt{get\_world\_resources()} & All available trees/stones remaining. & \texttt{Array[Dictionary]} \\
\texttt{get\_tick\_data()} & The active runtime tick state. & \texttt{int} \\
\bottomrule
\end{tabularx}
\caption{Sense API Methods}
\label{tab:sense_api}
\end{table}

\section{Sandbox Verification}
The provided test script independently asserts this logic by dispatching a \texttt{MOVE} scenario. It correctly confirms \texttt{is\_idle = false} during transit and relies purely on the \texttt{unit\_idled} signal callback to establish when it flips back to \texttt{is\_idle = true}. Console output is explicitly formatted as \texttt{[SENSE\_QUERY]}, \texttt{[UNIT\_IDLE]}, and \texttt{[DATA\_SNAPSHOT]}.

\end{document}
